A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-22 4_method.tex
new legend
explain that the method is only about the evenly distributed strategy

We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
explain how to identify central regions in \cref{sec_center_classification}.
Rounding the heights in the central mesh regions and smoothing those heights is handled in \cref{sec_central_height_adjustment}.
We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
In \cref{sec_generalization} we describe how to generalize our method into a general framework for generating contour parallel toolpaths using an arbitrary beading strategy and we show several such beading strategies.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{sources/method/terminology.pdf}
\caption{Explanation of terms.}
\label{legend}
\end{figure}

@@

This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
For skeletal segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization doesn't alter the extent and existence of marked central regions.
See \cref{discretization}.

>>>>

This section explains how we can generate toolpaths with evenly distributed bead widths.
We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
explain how to identify central regions in \cref{sec_center_classification}.
Rounding the heights in the central mesh regions and smoothing those heights is handled in \cref{sec_central_height_adjustment}.
We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading strategy and we show several such beading strategies.

@@

\begin{figure}\centering
\includegraphics[width=.75\columnwidth]{sources/method/legend2.pdf}
\caption{Explanation of terms and common color coding.}
\label{legend}
\end{figure}

@@

This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
For skeletal segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization doesn't alter the extent and existence of marked central regions.
See \cref{legend}.
